### 2021-06-17 written/eLifeRevision/Bittner_eLife2021.tex
latest edits

\textbf{Data availability statement}: \\
The datasets generated during and/or analyzed during the current study are available from the corresponding author upon reasonable request.

\textbf{Code availability statement}: \\
All software written for the current study is available at https://github.com/cunningham-lab/epi.

>>>>

\textbf{Data availability statement}: \\
The datasets generated during this study have been made publicly available on Zenodo at this address: 
https://doi.org/10.5281/zenodo.4910010 .

\textbf{Code availability statement}: \\
All software written for this study is available at https://github.com/cunningham-lab/epi .
